Multi-modality Imagery Database for Plant Phenotyping

### 2015-07-27 datapaper_conclusion.tex
1st revision edits

It might be noticed that all plants in MSU-PID belong to the same genotype and no treatments applied.
This is because we think a fundamental issue with visual phenotyping, i.e. accurate and automated identification and tracking of individual leaves over developmental time scales (weeks), which importance has being highlighted in Introduction, needs to be solved before expending our goal to define group differences.
The inherent challenge in this issue is that as leaves emerge and grow, they change in size, position and shape and they may overlap or be overlapped by other leaves.
We emphasize more in leaf identification and tracking rather than developing methods to define group differences.

For others to use our dataset, we have designed an experimental protocol with various evaluation metrics for different applications.  
To facilitate future research, we apply our automatic multi-leaf segmentation, alignment, and tracking algorithm on the fluorescence and RGB modalities of Arabidopsis imagery, where the labels for RGB modality is provided via label propagation. 
Our methods performs better on fluorescence images than RGB images. 
This is due to three reasons. 
First, the algorithm is originally developed for fluorescence images. 
Second, the resolution of RGB images are much lower than that of fluorescence images. 
Third, the groudtruth labels for RGB images are generated through the mapping of fluorescence labels, which will cause some error. 
We recognize our dataset as very challenging dataset.

>>>>

It might be noticed that all plants in MSU-PID belong to the same genotype and no treatments applied.
This is because we think a fundamental issue with visual phenotyping, i.e., accurate and automated identification and tracking of individual leaves over developmental time scales (weeks), whose importance has been highlighted in Section~\ref{sec:intro}, needs to be solved before expending our goal to define group differences.
The inherent challenge in this issue is that as leaves emerge and grow, they change in size, position and shape and they may overlap or be overlapped by other leaves.
We emphasize more in leaf segmentation, alignment and tracking rather than developing methods to discriminate group differences.

For others to use our dataset, we have designed an experimental protocol with various evaluation metrics for different applications.  
To facilitate future research, we apply our automatic multi-leaf segmentation, alignment, and tracking algorithm on the fluorescence and RGB modalities of Arabidopsis imagery, where the labels for RGB modality is provided via label propagation. 
The experimental results on fluorescence and RGB images indicate that our dataset is very challenging.
